---
title: "`r params$projectid` Status Report"
subtitle: "status_report.Rmd v 0.90.0"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    highlight: default
fontsize: 10pt
geometry: margin = 0.6in
params:
  projectid : not specified
  subjectid: not specified
  filename: not specified
---


```{r setup, include = F}
# initial setup
knitr::opts_chunk$set(cache       = F,
                      fig.width   = 12,
                      fig.height  = 5,
                      warning     = F,
                      message     = F,
                      tidy        = F,
                      prompt      = T,
                      strip.white = T,
                      comment     = NA)

stopifnot(length(params$filename) > 0)
stopifnot(length(params$projectid) > 0)
stopifnot(length(params$subjectid) > 0)

############################## EXAMPLE CALL ####################################
# rmarkdown::render("status_report.Rmd",
#  params=list(
#    filename = dir(".", c(".csv"), recursive = T),
#  output_file = paste("status_",
#                      format(Sys.time(), '%Y%m%d'), ".pdf", sep="")
# )
############################## EXAMPLE CALL ####################################
```

\hfill 

This report is intended to give a summary of analysis result of project 
`r params$projectid`. The result can be reproduced using the identical data 
files and identical version of rmarkdown file stated in the table below.  


Name                        Value
--------------------------  ----------------------
.Rmd version                v 0.90.0
Project name                `r params$projectid`
Subject id                  `r params$subjectid`
Data file                   `r params$filename`
--------------------------  ----------------------

\pagebreak

### Status Plot

Project process status plot.  
  
```{r plot1, echo = FALSE}
df <- read.csv(filename)
statusplot(df)

```

### Subject Summary

In total `r length(params$subjectid` subjects' data files have been anaylzed in this project.  
And the individual parameters are:
```{r sum1, echo = FALSE}
x <- table(df$var)
knitr::kable(matrix(x, byrow=T, nrow=1), col.names=names(x))

```


### Boxplot and Histogram (Daily Variables)

Statistical summary plots with dashed line representing location of mean.

```{r plot2, echo=F}
# Boxplot
par(mar=c(3,1,1,1))
p <- ggplot(df, aes(factor(var), var2))
p + geom_boxplot() + 
  geom_hline(aes(yintercept=mean(var2)), linetype="dashed", color="gray22", size=1) +
  coord_cartesian(ylim=c(0, 24)) + 
  scale_y_continuous(breaks=seq(0, 24, 6)) + 
  xlab("Var1") + 
  ylab("var2") + 
  ggtitle("Boxplot of Daily Variable")

par(mar=c(1,1,10,1))
# Histogram
p <- ggplot(df, aes(x=var2, fill=var))
p + geom_bar() + 
  geom_vline(aes(xintercept=mean(var2)), linetype="dashed", color="gray22", size=1)

```


\pagebreak


### Time Series Plot  

Time series plot, with smoothed conditional mean plotted (when samples < 1000, 
use method of local polynomial regression fitting; otherwise, use method of 
generalized additive models with integrated smoothness estimation) 

```{r plot3, echo=F, fig.height=10}
# Time Series Plot
p <- ggplot(df, aes(var1, var2))
p + geom_line(aes(color=factor(var1)), size=1) + 
  geom_smooth(color="gray45", size=1, linetype="dashed") + 
  facet_grid(var1  ~ .) + 
  theme(legend.position="none") + 
  coord_cartesian(ylim=c(0, 24)) + 
  scale_y_continuous(breaks=seq(0, 24, 6)) + 
  xlab("Time") + 
  ylab("Variable") + 
  ggtitle("Time Series Plot")

```



